A new metric for automatic data visualization for distributional difference in time series

### 2021-05-19 paper/main-old.Rmd
fixed wrong plots

```{r glm-tab}
broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
```

>>>>

```{r glm-tab,eval=FALSE}
broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
```
